---
title: "R_attack"
author: "Minajia ZHU"
date: "Tuesday, January 20, 2015"
output: word_document
---


```{r,echo=FALSE,warning=FALSE}
options(xtable.comment = FALSE)
library("knitr")
library("formatR")
opts_chunk$set(message=F,comment="",tidy=T,warning=FALSE,highlight=TRUE)

```



## 预处理

1.读取任何形式的数据(包括mp3数据):

> G:\\R\\datascience\\Getting and Cleaning Data\\quiz2

2.展示数据结构和概况:

```
list.dir()
list.files() 
ls.str()
```

```{r}
plot(airquality)#二维散点图
boxplot(airquality)#框须图
summary(airquality)
str(airquality)
attributes(airquality)
attr(airquality,"row.names")
```

3.
```{r}
x = c(1,2,"cat",3);x
mode(x)
y = c(5,T,3,7);y
mode(y)

```

4.全局设置

```{r}
names(options())

```

5.保存变量和读取变量

```
#前者保存全部变量，后者保存指定变量
save.image()
save(变量x,变量y,变量z, file = "mydata.rda")
load("mydata.rda")

```

6.输入与输出

```
#文本输出
sink("test.txt",append = T, SPLIT = T)
#图片输出
pdf("test.pdf"")
    
head(CO2)
dev.off()

write.table(CO2,file = "co2.txt", row.names = F,col.names = F,sep = ",")

#输出 LATEX 格式的表格还可以 quantreg 包中的 latex.table()函数
#从其他程序读取数据,采用foreign包

```
```{r}
#调用R的输出信息
glmout = capture.output ( example ( glm ) )
glmout [ 1 : 5 ]

```

7.调用R的输出信息

```{r}
glmout = capture.output(example ( glm ) )
glmout[1:5]

```

8.字符串转变为命令行

```{r}
x = 1:10
a = "print(x)"
class(a)
eval(parse(text = a))
```



## 数据操作

### 基础

**读取数据**

```
options(stringsAsFactors = F)
read.table(file, col.names = c(), row.names = NULL, as.is = 索引向量(哪些变量不被转换成因子) / 与变量长度相符的逻辑向量 / TRUE(全部不转换),
 na.strings = , comment.char = '', encoding = 其他字符, skip = , nrows = 想要读取的行数 ,fill = TRUE(用count.fields来确定问题所在), 
 colClasses = 字符向量 / "NULL"指跳过某列 / NA指默认设置)

#若要读取相同宽度的不规则数据,使用read.fwf函数
```

```
#读取xls数据
library(RODBC)
z <− odbcConnectExcel ( ”.xls” )
dd <− sqlFetch ( z , ” Sheet1 ” )
close(z)

#读取剪切版数据
mydata = read.delim("clipboard")

```

**检验两组向量或者数据框是否都为完整的，或者不同**

```{r}

#数据框是否完整
x <- c(1, 2, NA, 4, NA, 5)
y <- c("a", "b", NA, "d", "e",NA)
complete.cases(x,y)

airquality[1:6, ]
good <- complete.cases(airquality)
airquality[good, ][1:6, ]

```

```
#数据框的元素不同
identical( a1 , a2 )
which ( a1 !=a2 , arr.ind = TRUE) #arr.ind为array.indices

```
**去掉多余元素**

```
x = c (9 : 20 , 1 : 5 , 3 : 7 , 0 : 8 )
( xu = x [ !duplicated(x) ] )
unique (x) 
#is more efficient

#删除list中的元素
lst = list(a = list(b = 1,c = 2), b = list(d = 3,e = 4))
lst$a$b = NULL
```

**缺失值的处理**

```
x[!is.na(x)]
na.omit()
对于统计慨括函数,mean,var等,可使用参数na.rm = T
```

**关于挑选数据**

```
subset ( iris , select = c ( Sepal.Length , Petal.Length ) ,
Species == ”setosa” )

```

```{r}

set.seed(13435)
X <- data.frame("var1"=sample(1:5),"var2"=sample(6:10),"var3"=sample(11:15))
X <- X[sample(1:5),]; X$var2[c(1,3)] = NA
X[(X$var1 <= 3 | X$var3 > 15),]

X[1:2,"var2"]
X[which(X$var2 > 8),]

sort(X$var2,na.last=TRUE)
X[order(X$var1,X$var3),]

library(plyr)
arrange(X,var1)
arrange(X,desc(var1))

X$var4 <- rnorm(5)
Y <- cbind(X,rnorm(5))

```

**合并数据框**

```
merge(x,y,by.x = ,by.y = ,all = )

```


**简单的数据生成**

```{r}

rep(1:5,each = 2)
rep(1:5,time = 2)
seq(1,10,by = 2)
seq(1,10,length = 3)

#追加元素
x = 1:5
( foo = c ( x [ 1 ] , 0 , x [ 2 : 5 ] ) ) # expected r e s u l t
append ( x , 0 , after = 1)

```

**数据标准化**
```{r}

x = c(rnorm(100),2*rnorm(30))
m = scale(x,scale = F) #only centering
n = scale(x,center = F) #only scaling

```



**抽样**

```
sample(x)
sample(x,replace = T)
sample(x,n)
sample(x,n,replace = T)
sample(x,n,replace = T,prob = p)
```



**生成因子,转化为数字**

```{r}

#因子的基础知识

data = c(1,2,2,3,1,2,3,3,1,2,3,3,1)
fdata = factor(data)
levels(fdata) = c('I','II','III')

#有序因子

mons = factor('march','april','august',
         levels = c('april','march','august'),
         order = T)

#对因子重新排序

with(InsectSprays,
     reorder(spray,count,mean)
     )

#gl(x,y) x为所需生成不同因子的数目，y为重复的次数

thelevels = data.frame(group=gl(3,10,length=30),
       subgroup=gl(5,2,length=30),
       obs=gl(2,1,length=30))

#第一个因子乘以第二个因子

expand.grid(seq(1,5,by = 2),seq(2,5,by = 2))
```

```
as.numeric(as.charactor(x))

```

**两组平行向量的极值**

```{r}
x= 1:10
y = rev(x)
pmax(x,y)
pmin(x,y)

```




**维度变换**

```
x = array(1:24, 2:4)
xt = aperm(x,c(2,1,3))
dim(x) ; dim(xt)

```

**序列转矩阵**

```{r}

x = 1:10
t(x);class(t(x))
t(t(x));class(t(t(x)))

```


**序列的处理**

```{r}
#rle()为游程处理
seq1 = c(1,3,5,2,4,2,2,2,7,6)
rle.seq1 = rle(seq1)
rle.seq1
any(rle.seq1$values == 2 & rle.seq1$length >= 3)

```

**时间序列**


```{r}

ts(1:47,frequency = 4,start = c(1959,2))

```



**矩阵**

```{r}

rmat = matrix(rnorm(15),5,3,dimnames = list(NULL,c('A','B','C'))) 
rmat

# 或者

rmat = matrix(rnorm(15),5,3)
dimnames(rmat) = list(NULL,c('A','B','C'))
rmat

 #矩阵乘法,crossprod(X,y)
outer(month.abb, 1999:2003, FUN = "paste") #outer的使用


```

----------

###探索性数据分析

```
barplot(as.table(x))

hist(x,breaks = 100)


```


----------

Writing for, while loops is useful when programming but not particularly easy when working interactively on the command line. There are some functions which implement looping to make life easier.

* lapply: Loop over a list and evaluate a function on each element
* sapply: Same as lapply but try to simplify the result
* apply: Apply a function over the margins of an array
* tapply: Apply a function over subsets of a vector
* mapply: Multivariate version of lapply

An auxiliary function split is also useful, particularly in conjunction with lapply.


### example:

### sapply

```{r}
#x可以为dataframe,list或者向量
x <- 1:4
lapply(x, runif, min = 0, max = 10)

x <- list(a = matrix(1:4, 2, 2), b = matrix(1:6, 3, 2)) 
lapply(x, function(elt) elt[,1])
```


### mapply

```{r}
noise <- function(n, mean, sd) {
 rnorm(n, mean, sd)
 }
noise(5, 1, 2)
mapply(noise, 1:5, 1:5, 2)
```

### tapply(用于向量,而aggregate用于数据框)

```{r}
x <- c(rnorm(10), runif(10), rnorm(10, 1))
f <- gl(3, 10)
f
tapply(x, f, mean)

attach ( warpbreaks )
tapply ( breaks , list ( wool , tension ) , mean)

aggregate ( breaks , list ( wool , tension ) , mean)

```

### split

```{r}
s <- split(airquality, airquality$Month)
lapply(s, function(x) colMeans(x[, c("Ozone", "Solar.R", "Wind")]))
sapply(s, function(x) colMeans(x[, c("Ozone", "Solar.R", "Wind")],
                                 na.rm = TRUE))


```


---------------

## lattice

```{r}
library(lattice)
## Convert 'Month' to a factor variable
airquality <- transform(airquality, Month = factor(Month))
xyplot(Ozone ~ Wind | Month, data = airquality, layout = c(5, 1))

```

```{r}
set.seed(10)
x <- rnorm(100)
f <- rep(0:1, each = 50)
y <- x + f - f * x + rnorm(100, sd = 0.5)
f <- factor(f, labels = c("Group 1", "Group 2"))
xyplot(y ~ x | f, layout = c(2, 1))  ## Plot with 2 panels
```

```{r}
## Custom panel function
xyplot(y ~ x | f, panel = function(x, y, ...) {
    panel.xyplot(x, y, ...)  ## First call the default panel function for 'xyplot'
    panel.abline(h = median(y), lty = 2)  ## Add a horizontal line at the median
})

## Custom panel function
xyplot(y ~ x | f, panel = function(x, y, ...) {
    panel.xyplot(x, y, ...)  ## First call default panel function
    panel.lmline(x, y, col = 2)  ## Overlay a simple linear regression line
})
```

----------

## 数学运算

**积分**

```{r}

integrate(dnorm , -1.96 , 1.96)
integrate(dnorm , -Inf , Inf )
fun = function(x) {x^2}
integrate(fun,lower = 0,upper = 2)

```

