---
title: "R_attack"
author: "Minajia ZHU"
date: "Tuesday, January 20, 2015"
output: html_document
---


```{r,echo=FALSE,warning=FALSE}
options(xtable.comment = FALSE)
library("knitr")
opts_chunk$set(message=F,comment="",tidy=T,warning=FALSE,highlight=TRUE)

```


Writing for, while loops is useful when programming but not particularly easy when working interactively on the command line. There are some functions which implement looping to make life easier.

* lapply: Loop over a list and evaluate a function on each element
* sapply: Same as lapply but try to simplify the result
* apply: Apply a function over the margins of an array
* tapply: Apply a function over subsets of a vector
* mapply: Multivariate version of lapply

An auxiliary function split is also useful, particularly in conjunction with lapply.


**example**

*sapply*:

```{r}
x <- 1:4
lapply(x, runif, min = 0, max = 10)

x <- list(a = matrix(1:4, 2, 2), b = matrix(1:6, 3, 2)) 
lapply(x, function(elt) elt[,1])
```


*mapply*:

```{r}
noise <- function(n, mean, sd) {
 rnorm(n, mean, sd)
 }
noise(5, 1, 2)
mapply(noise, 1:5, 1:5, 2)
```

*tapply*:

```{r}
x <- c(rnorm(10), runif(10), rnorm(10, 1))
f <- gl(3, 10)
f
tapply(x, f, mean)
```

*split*:

```{r}
s <- split(airquality, airquality$Month)
lapply(s, function(x) colMeans(x[, c("Ozone", "Solar.R", "Wind")]))
sapply(s, function(x) colMeans(x[, c("Ozone", "Solar.R", "Wind")],
                                 na.rm = TRUE))


```

